\TheTitle

### 2016-04-25 linvis.tex
added tree model to the paper

This representation works in smaller projects; it enables users to see
when changes are made, when these changes are merged, and how each branch is
interacting.  
In large modular projects, like the Linux kernel, the DAG becomes a
mess of merges and commits (figure \ref{fig:gitk}) losing its visual meaning.  In
some cases, the Linux kernel is simply too large for the system to generate a
visualization (eg. Github provides a DAG view for many projects, but is unable to
display the visualization for projects as large as the Linux kernel (figure
\ref{fig:gitfail}).
Furthermore, Linux creates between 60 and 70k new commits every year and, according to \cite{emsePaper}, 
a commit a median of YYYY days to arrive to the official repository from the moment it is authored. 
This means that, if a person inspected the commits in this repository today, tomorrow it might contain  hundreds
of commits that were authored months ago. However, distinguishing these new commits is not trivial.

@@

One of the challenges with visualzing the arrival of commits to a repository is that
in Git, commits are immutable, and Git does not store the date that a commit was merged into another branch (including master)
To complicate the problem, the DAG points to the ancestors of a commit (a model necessary for the operation of Git), but developers 
would prefer to know the path that a commit followed to reach the master repository. \dmg{perhaps a figure is good here}.
In the context of Linux tracing the path that a commit followed to master would imply that for any given merge, it would be possible to know what commits were merged.
With such a feature,  a user
could inspect the commits that have arrived into master within a given time frame.
 and decide that it is important.

@@

 The contributions of this paper are two. First, we describe a method to convert the DAG of the Linux repository into a tree (we call this the tree model of the
 reposisory) that represents the path used by
 any commit to reach master. Second, 
 we present a method to inspect and visualize the history of merges in the  Linux project using the tree-model of the repository

@@

@@

To our knowledge, we know of no git repository visualization tool that builds
trees from the DAG provided by git. This may be because more information is required
to generate the trees than what is stored by git. Git uses a DAG model, which
enables history-altering actions, like rebases to occur, whereas older tools like
CVS and svn construct trees\cite{CVS2008} but do not work with history-altering
actions.

A server must sit and monitor the git repository as it changes over time to record
the changes to history. Many of the visualization tools are designed for a
general-purpose approach, where any repository is directly usable without additional
information. Polling for this additional information makes the visualizer specific
to a repository or project.

@@

Gitk, Gitg, and other similar git repository visualization tools use the DAG as the
central organization model. This model is sufficient for smaller projects, providing
meaningful information; however, in larger projects, like the Linux kernel, the
branches become too tangled and too deep to derive any meaning from the DAG. Users
can interact with the DAG by going to the previous commit in the chain or jumping to
the parent merge. This suggests that Gitk and similar tools are designed for users
working from a given commit or leaf-node toward the root. With this model, it is
difficult for users to see what other commits are involved within a given merge.

>>>>

This representation works in smaller projects; it enables users to see
when changes are made, when these changes are merged, and how each branch is
interacting.  
In large modular projects, like the Linux kernel, the DAG becomes a
mess of merges and commits (figure \ref{fig:gitk}) losing its visual meaning.  In
some cases, the Linux kernel is simply too large for the system to generate a
visualization (eg. Github provides a DAG view for many projects, but is unable to
display the visualization for projects as large as the Linux kernel (figure
\ref{fig:gitfail}).
Furthermore, Linux creates between 60 and 70k new commits every year and, according to our previous work \cite{German2015}, 
a commit takes a median of 30 days (from the moment it is authored) to the time it arrives to the official repository
This means that, if a person inspected the commits in this repository today, tomorrow it might contain  many more
of commits that were authored long before. However, distinguishing these new commits is not trivial.

@@

One of the challenges with visualizing the arrival of commits to a repository is that
in Git, commits are immutable, and Git does not store the date that a commit was merged into another branch (including master).
To complicate the problem, the DAG points to the ancestors of a commit (a model necessary for the operation of Git), but developers 
would prefer to know the path that a commit followed to reach the master repository. \dmg{perhaps a figure is good here}.
Hence, tracing the path that any commit followed to master would imply that for any given merge, it would be possible to know what commits were merged. A user could
inspect the commits that have arrived into master within a given time frame by simply checking which commits where merged during that time frame.

@@

 The contributions of this paper are two. First, we describe a method to convert the DAG of the Linux repository into a tree (we call this the \emph{tree-model of the
 repository}) that represents the path used by
 any commit to reach master. Second, 
 we present a method to inspect and visualize the history of merges in the  Linux project using the tree-model of the repository

@@

\section{Data model}

Git uses a Directed Acyclic Graph (DAG) as its main data model. In this model, a commit has one or more ordered parents (ancestors), except the root commits of a repository which
do not have ancestors--Linux git repository has two such commits. Commits are divided into merge commits (they merge two or more branches) and non-merge
commits. Non-merge commits have only once parent, while merge commits have two or more. The order of the parents matter: the first parent is the branch in which
the merge is being done; while the rest indicate the branches being merged (git allows any number of branches to be merged at the same time). Their order in the
parents relationship indicate the order in which the branches are being merged (second parent first, third parent second, etc.).

In Git commits are immutable. Once they are created, they never change. Git allows operations to alter commits or to reorder them. However, in such case, the
commit changes its commit id, effectively becoming a new commit. This means that commits do not record the branches or repositories they have traversed in their
way to master. 
For instance, assume the sequence of commits  exemplified in Figure~\ref{fig:repoEvents}. In this case commits are performed in various repos and branches. The
DAG representation of these commits is shown in Figure~\ref{fig:repoDAG}. Notice that this DAG loses information about what repository is Master (in fact, it
loses all information about what repositories any commit has passed through). The tree-model of this DAG is shown in Figure~
\ref{fig:reposTree}. Note that the direction edges of the DAG have been inverted. Instead of pointing to the ancestors, it points to its successors (the path to
Master). Also, the DAG has been simplified, and it only shows for any commit, one edge (its path to Master).

\subsection{Computing the tree-model of the DAG of Linux}

Computing the tree-model of a DAG of any repository might not be possible. However, certain features of the development process of Linux make it possible to
compute the its tree model. In particular, the Master branch of Linux is maintained by Linus Torvalds and only him has write access to it. We have verified this
assertion if previous research~\cite{German2015}.

\dmg{I'll continue after dinner}

\evanTodo{Move related work to the end, try to match the text of the paper to my intro}

\begin{figure}[htbp]
  \centering
        \includegraphics[width=\columnwidth]{figures/events.pdf}
  \caption{Example of a sequence of events performed in different repositories. The horizontal axis represents time. Each horizontal section represents a
    different branch and/or repository. Each commit points to its ancestor.}
  \label{fig:repoEvents}
\end{figure}

\begin{figure}[htbp]
  \centering
        \includegraphics[width=.8\columnwidth]{figures/dag.pdf}
  \caption{DAG representation of the commits represented in Figure~\ref{fig:repoEvents}. It loses information about what repository the commit is performed and
    through which repositories it has passed in its way to Master. In fact, the DAG does not even know what Master is.}
  \label{fig:repoDAG}
\end{figure}

\begin{figure}[htbp]
  \centering
        \includegraphics[width=\columnwidth]{figures/tree.pdf}
  \caption{Tree-model of the commits  represented in Figure~\ref{fig:repoEvents} showing the path they followed to reach master. In this model the successors of
    each commit represents the path followed by that commit to reach Master.}
  \label{fig:repoTree}
\end{figure}

@@

To our knowledge, we know of no git repository visualization tool that builds
a tree that maps the path commits follow to master
from the DAG provided by git. This may be because more information is required
to generate the tree-model than what is stored by git. % Git uses a DAG model, which
% enables history-altering actions, like rebases to occur, whereas older tools like
% CVS and svn construct trees\cite{CVS2008} but do not work with history-altering
% actions.

% A server must sit and monitor the git repository as it changes over time to record
% the changes to history. Many of the visualization tools are designed for a
% general-purpose approach, where any repository is directly usable without additional
% information. Polling for this additional information makes the visualizer specific
to a repository or project.

@@

Gitk, Gitg, and other similar git repository visualization tools use the DAG as the
central organization model. This model is sufficient for smaller projects, providing
meaningful information; however, in larger projects, like the Linux kernel, the
branches become too tangled and too deep to derive any meaning from the DAG. Users
can interact with the DAG by going to the previous commit in the chain or jumping to
the parent merge. Given the direction that each node in the DAG has (pointing to its parent)
it can be assumed that tools that exploit the DAG (such as gitk and similar tools) are designed for users
working from a given commit towards the past. Working in the opposite direction is hard, since merge commits provide multiple paths towards the present, with no
way to distinguish which path is the one used by the current commit to be merged into master.
